The problem and promise of scale in multilayer networks

### 2020-02-03 paper/manuscript.Rmd
fix output fig width to linewidth

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    # warning = FALSE,
    # message = FALSE,
    eval = TRUE
)

library(knitcitations)
options("citation_format" = "pandoc")

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    # warning = FALSE,
    # message = FALSE,
    eval = TRUE,
    out.width = '\\linewidth'
)
